Inverse Problems --- Example Sheet 2

### 2020-11-16 distribution_theory/distribution_ES2.tex
pffft

% Functions that appear frequently
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\Int}{Int}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\ord}{ord}

@@

	Suppose $u$ is compactly supported. Since $\refl{v * \refl\phi} \in \EE(\RR^n)$, there exists a compact $K \subseteq X$ and nonnegative $C, N$ such that
	\begin{align*}
		\abs{\ang{u, \refl{v * \refl\phi}}} &\leq C \sum_{\alpha \leq N} \sup_{x \in K} \abs{\pt^\alpha (\refl{v * \refl\phi})} = C \sum_{\alpha \leq N} \sup_{x \in -K} \abs{\pt^\alpha (v * \refl\phi)} = C \sum_{\alpha \leq N} \sup_{x \in -K} \abs{v * \pt^\alpha\refl\phi}\\
		&= C \sum_{\abs{\alpha} \leq N} \sup_{x \in -K} \abs{\ang{v, \tau_x \refl{\pt^\alpha \refl\phi}}}.
	\end{align*}
	Note that if $\supp\phi \subseteq K'$, then $\supp\refl\phi \subseteq -K'$, and for $x \in -K$ we find $\supp \tau_x \refl{\pt^\alpha \refl\phi} \subseteq -K' -K$. Then by the previous equation we find that there exists $C', M$ with
	\[
	\abs{\ang{u * v, \phi}} \leq C' \sum_{\abs{\alpha} \leq N} \sum_{\abs{\beta} \leq M} \sup_{x \in -K' - K} \pt^\beta (\tau_x \refl{\pt^\alpha \refl\phi}) = C' \sum_{\abs{\alpha} \leq N} \sum_{\abs{\beta} \leq M} \sup_x \abs{\pt^{\alpha + \beta} \phi} \leq C'' \sum_{\abs{\alpha} \leq M + N} \sup_x \abs{\pt^\alpha \phi},
	\]
	which shows that $u* v \in \DD'(\RR^n)$. An analogous argument holds if $v$ is compactly supported. 
\end{proof}

@@

\begin{proof}
	Let $\psi \in \DD(\RR)$, then we want to prove that \[
	\psi(x) = \frac1{(2\pi)^n} \iint e^{i \lambda (x - y)} \psi(y) \dd{y} \dd{\lambda}. 
	\]
	??
\end{proof}

@@

\begin{proof}
	We have
	\begin{align*}
		\sum_m \phi(m) = \frac1{(2\pi)^n} \sum_m \int e^{i\lambda m} \hat \phi(\lambda) \dd{\lambda} = \sum_m \int e^{2\pi i \lambda m} \hat \phi(2\pi \lambda) \dd{\lambda}
	\end{align*}
\end{proof}
\end{document}

>>>>

% Functions that appear frequently
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\Int}{Int}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\ord}{ord}
%\DeclareMathOperator{\PV}{PV}

@@

	Suppose $u$ is compactly supported. Since $\refl{v * \refl\phi} \in \EE(\RR^n)$, there exists a compact $K \subseteq X$ and nonnegative $C, N$ such that
	\begin{align*}
		\abs{\ang{u, \refl{v * \refl\phi}}} &\leq C \sum_{\alpha \leq N} \sup_{x \in K} \abs{\pt^\alpha (\refl{v * \refl\phi})} = C \sum_{\alpha \leq N} \sup_{x \in -K} \abs{\pt^\alpha (v * \refl\phi)} = C \sum_{\alpha \leq N} \sup_{x \in -K} \abs{v * \pt^\alpha\refl\phi}\\
		&= C \sum_{\abs{\alpha} \leq N} \sup_{x \in -K} \abs{\ang{v, \tau_x \refl{\pt^\alpha \refl\phi}}}.
	\end{align*}
	Note that if $\supp\phi \subseteq K'$, then $\supp\refl\phi \subseteq -K'$, and for $x \in -K$ we find $\supp \tau_x \refl{\pt^\alpha \refl\phi} \subseteq -K' -K$. Then by the previous equation we find that there exists $C', M$ with
	\[
	\abs{\ang{u * v, \phi}} \leq C' \sum_{\abs{\alpha} \leq N} \sum_{\abs{\beta} \leq M} \sup_{x \in -K' - K} \pt^\beta (\tau_x \refl{\pt^\alpha \refl\phi}) \leq C' \sum_{\abs{\alpha} \leq N} \sum_{\abs{\beta} \leq M} \sup_x \abs{\pt^{\alpha + \beta} \phi} \leq C'' \sum_{\abs{\alpha} \leq M + N} \sup_x \abs{\pt^\alpha \phi},
	\]
	which shows that $u* v \in \DD'(\RR^n)$. An analogous argument holds if $v$ is compactly supported. 
\end{proof}

@@

\begin{proof}
Since $\DD(\RR) \subseteq \SS(\RR)$, we know that the Fourier inversion formula holds. We only need to show that the Fourier tranform of $\phi$ is again an element of $\DD(\RR)$. (??)
\end{proof}

@@

\begin{proof}
	We have
	\begin{align*}
		\sum_m \phi(m) = \frac1{(2\pi)^n} \sum_m \int e^{i\lambda m} \hat \phi(\lambda) \dd{\lambda} = \sum_m \int e^{2\pi i \lambda m} \hat \phi(2\pi \lambda) \dd{\lambda}
	\end{align*}
(??)
\end{proof}

\begin{question}
	If $u \in H^s(\RR^n)$ show that $D^\alpha u\in H^{s - \abs{\alpha}} (\RR^n)$. If $s > t$ show that $H^s(\RR^n) \subseteq H^t(\RR^n)$. 
\end{question}

\begin{proof}
	Assuming $u \in H^s(\RR^n)$, we have
	\begin{align*}
		\int_{\RR^n} \ang{\lambda}^{2(s - \abs{\alpha})} \abs{\widehat{D^\alpha u}(\lambda)}^2 \dd{\lambda}  &= \int_{\RR^n} \ang{\lambda}^{2(s-\abs{\alpha})} \norm{\lambda}^{2\abs{\alpha}} \abs{\hat u(\lambda)}^2 \dd{\lambda} \\
		&\les \int_{\RR^n} \ang{\lambda}^{2s} \abs{\hat u(\lambda)}^2 \dd{\lambda} < \infty, 
	\end{align*}
which proves $D^\alpha u \in H^{s- \abs{\alpha}}(\RR^n)$.

The second claim follows immediately from the fact that $\ang{\lambda}^{t} \leq \ang{\lambda}^s$ for $s \geq t$ and $\lambda$ sufficiently large. 
\end{proof}

\begin{question}
	Show that $S(\RR^n)$ is dense in $L^2(\RR^n) = H^0(\RR^n)$ and deduce that $\SS(\RR^n)$ is dense in $H^s(\RR^n)$.

	\emph{Hint:} Use Parseval's theorem. 
\end{question}

\begin{proof}
	We will show that $\DD(\RR^n)$ is dense in $L^2(\RR^n)$: since $\DD(\RR^n) \subseteq \SS(\RR^n)$, this shows that $\SS(\RR^n)$ is dense in $L^2(\RR^n)$ as well.

	\TODO Give proof.

	Now, for $u \in H^s(\RR^n)$, let $(\phi_m) \to u$ in $L^2$. Then we have
	\begin{align*}
		\norm{\phi_m - u}_{H^s}^2 = \int \ang{\lambda}^{2s} \abs{(\phi_m - u)(\lambda)}^2 \dd{\lambda}
	\end{align*}
\end{proof}
%-----------------------------------------------------------------------------
\setcounter{question}{18}

\begin{question}
	Compute the Fourier transforms of the functions
	\begin{enumerate}[(a)]
		\item $\sign(x)$;
		\item $\arctan(x)$;
		\item $x\log \abs{x} - x$;
		\item $\exp(i\omega x^2)$
	\end{enumerate}
	in $\SS'(\RR)$, where $\omega \in \RR$. 
\end{question}

\begin{proof}
	\begin{enumerate}[(a)]
		\item We have for $\phi \in \SS(\RR)$ that 
		\begin{align*}
			\ang{\widehat{\sign}, \phi} &= \ang{\sign, \hat\phi} = \int_\RR \sign(\lambda) \hat\phi(\lambda)\dd{\lambda} = \int_\RR \sign(\lambda) \int_\RR e^{-i\lambda x} \phi(x) \dd{x} \dd{\lambda}
			\\
			&\overset\star= \int_\RR \phi(x) \int_\RR \sign(\lambda) e^{-i\lambda x} \dd{\lambda} \dd{x} 
			=  \int_\RR \phi(x) \lim_{R\to\infty} \qty(\int_0^R e^{-i\lambda x} \dd{\lambda}  -  \int_{-R}^0 e^{-i\lambda x}  \dd{\lambda})\dd{x} \\
			&= \lim_{\eps\to0} \lim_{R\to\infty} \int_{\abs{x}>\eps}  \phi(x) \qty(\frac{e^{ix R} + e^{-ix R}}{ix} - \frac2{ix}) \dd{x}  \\
			&= \lim_{\eps \to 0} \lim_{R\to\infty} \int_\RR \frac{\phi(x) \ind_{\abs{x}> \eps}}{ix} \cdot e^{ixR} \dd{x} + \lim_{\eps \to 0} \lim_{R\to\infty} \int_\RR \frac{\phi(x) \ind_{\abs{x}> \eps}}{ix} \cdot e^{-ixR} \dd{x} + 2i \PV\qty(\frac1x).
%			&= \lim_{R\to\infty}\qty( \int_\RR \phi(x) \int_0^R e^{-i\lambda x}\dd{x} - \int_\RR \phi(x) \int_{-R}^0 e^{-i\lambda x} \dd{x})
		\end{align*}
	We claim the first two terms go to 0: this is because the term in the integral is the Fourier transform of $\frac{\phi(x)\ind_{\abs{x} > \eps}}{ix}$ evaluated at $\pm R$, and since the function is in $L^1$, its Fourier transform decays to 0 as $\abs{R} \to\infty$.

	We conclude $\widehat\sign = 2i \PV(\frac1x)$.

	\item We know that $\arctan'(x) = \frac{1}{1 + x^2} \eqqcolon f(x)$, then we have $\widehat\arctan(\lambda) = \frac1{i\lambda} \hat f(\lambda)$ (in the distributional sense).

	We have, using Fubini and the fact that $\ang{\hat f, \phi}$ is finite, that 
	\begin{align*}
		\ang{\hat f, \phi} &= \int_\RR \frac{\hat\phi(\lambda)}{1 + \lambda^2} \dd{\lambda} = \int_\RR \phi(x) \lim_{R\to\infty} \int_{-R}^R \frac{e^{-i\lambda x}}{1 + \lambda^2} \dd{\lambda} \dd{x} \overset\star= \int_\RR \phi(x) \qty(\pi e^{-\abs{x}}) \dd{x}, 
	\end{align*}
	from which it follows that the Fourier transform of $\frac{1}{1 + x^2}$ is given by $\pi e^{-\abs{\lambda}}$, and therefore the Fourier transform of $\arctan$ is given by $\frac{\pi}{i\lambda} e^{-\abs{\lambda}}$.

	\item The derivative of this function, outside of 0, is $\log\abs{x}$.

	\item  Clearly, if $\omega = 0$, the function is 1 and its Fourier transform is $2\pi\delta_0$, so assume $\omega \neq 0$. 
	We have analogously to (b), with $f(x) = \exp(i\omega x^2)$, that 
	\[
	\ang{\widehat{f}, \phi} = \int_\RR \hat\phi(\lambda) e^{i\omega \lambda^2} \dd{\lambda} = \int_\RR \phi(x) \lim_{R\to\infty} \int_{-R}^R e^{i\omega\lambda^2 - i\lambda x} \dd{\lambda} \dd{x}.
	\]
	Now, by completing the square we have
	\[
	i(\omega\lambda^2 - x\lambda) = i\qty(\sqrt\omega\lambda - \frac{x}{2\sqrt\omega})^2 - \frac{ix^2}{4\omega},
	\]
	and therefore
	\begin{align*}
	\lim_{R\to\infty} \int_{-R}^R e^{i\omega\lambda^2 - i\lambda x} \dd{\lambda} &= e^{-ix^2/(4\omega)} \lim_{R\to\infty} \int_{-R}^R e^{i(\sqrt\omega\lambda - \frac{x}{2\sqrt\omega})^2}\dd{\lambda} = \frac{e^{-ix^2/(4\omega)}}{\sqrt\omega} \lim_{R\to\infty} \int_{-R}^R e^{i\lambda^2} \dd{\lambda} \\
	&= \frac{e^{-ix^2/(4\omega)}}{\sqrt\omega} (1+i)\sqrt{\frac\pi2}, 
	\end{align*}
	where we use that the \emph{Fresnel integral} $\int_{-\infty}^\infty e^{ix^2} \dd{x}$ is known.

	Plugging this back into our original equation yields
	\[
	\ang{\hat f, \phi} = \int_\RR \phi(x) \frac{e^{-ix^2/(4\omega)}}{\sqrt\omega} (1+i)\sqrt{\frac\pi2} \dd{x}, 
	\]
	which shows that
	\[
	\hat f(\lambda) =  (1+i) e^{-i\lambda^2/(4\omega)} \sqrt{\frac{\pi}{2\omega}}. 
	\]
	in the distributional sense. 
	\end{enumerate}
\end{proof}
\end{document}

### 2020-11-16 inverse_problems/inverse_ES2_handin.tex
pffft

\item Let $f \in L^1(\Omega) \setminus \BV(\Omega)$, then clearly $\pt \TV(f) = \emptyset$. Now suppose $f \in \BV(\Omega)$.  It is known that the dual of $L^1(\Omega)$ is $L^\infty(\Omega)$. Therefore, we have for $p \in L^\infty(\Omega)$ that 
\begin{align*}
	p \in \pt \TV(f) &\iff \TV(g) \geq \TV(f) + \int_{\Omega} p(x) (g - f)(x) \dd{x} \ \forall g \in L^1(\Omega)
\end{align*}
(??)
\end{enumerate}
\end{solution}

\begin{question}
	Let $\UU$ be a Banach space and let $E \colon \UU\to \rext$ be proper, lower semi-continuous and convex. Then the \emph{Fenchel conjugate} or \emph{convex conjugate} of $E$ is defined to be the mapping $E^* \colon \UU^* \to \RR$ with
	\[
	E^*(v) \ceq \sup_{u \in \UU} \qty{\ang{v, u} - E(u)}. 
	\]
	\begin{enumerate}[(a)]
		\item Compute the convex conjugates of the following functionals.
		\begin{enumerate}[(i)]
			\item $E(u) = \norm{u}_\UU$ for a Banach space $\UU$,
			\item $E(u \mid f) = \sum_{i=1}^n u_i \log(\frac{u_i}{f_i})$, where $f \in \RR^n_{>0}$ is a positive vector and $u \in \RR^n$. What is the effective domain of $E$? 
		\end{enumerate}
	\item Let $E \colon \UU\to\rext$ be a proper, lower semi-continuous and convex functional. Show that
	\[
	p \in \pt E(u) \iff u \in \pt E^*(p)
	\]
	for all $u, p \in \UU$.

	\emph{Hint:} You may exploit the fact that under the stated assumptions $E = E^{**}$ holds true. 
	\end{enumerate}
\end{question}

\begin{solution}
	\begin{enumerate}[(a)]
		\item \begin{enumerate}[(i)]
			\item We have
			\[
			E^*(v) = \sup_{u \in \UU} \qty(\ang{v, u} - \norm{u}). 
			\]
			Suppose $\ang{v, u^*} - \norm{u^*} = \xi > 0$ for some $u^*$. Then we have for $\alpha > 0$ that
			\[
			\ang{v, \alpha u^*} - \norm{\alpha u^*} = \alpha \qty(\ang{v, u^*} - \norm{u^*}) = \alpha\xi, 
			\]
			and therefore clearly $E^*(v) = \infty$.

			On the other hand, if $\ang{v, u} - \norm{u}\leq0$ for all $u$, then the supremum is attained in $u = 0$ with value $0$, and therefore $E^*(v) = 0$.

			We see that
			\begin{align*}
				&\ang{v, u^*} - \norm{u^*} > 0 &\text{for some $u^* \in \UU$}; \\
				&\iff \ang{v, u^*} > \norm{u^*} &\text{for some $u^* \in \UU$}; \\
				&\iff \norm{v}_{\UU^*} > 1. 
			\end{align*}
		We conclude that
		\[
		E^*(v) = \chi_\qty{\norm{v} \leq 1} = \begin{cases}
			0 &\text{if $\norm{v} \leq 1$}, \\ \infty &\text{else.}
		\end{cases}
		\]

		\item Suppose first that $p \in \pt E(u)$. Then we have
		\begin{align*}
&\phantom{\implies}	p \in \pt E(u) \\
&\implies E(v) \geq E(u) + \ang{p, v - u} &\text{for all $v$} \\
&\implies \ang{p, u} - E(u) \geq \ang{p, v} - E(v) &\text{for all $v$} \\
&\implies \ang{p, u} - E(u) \geq \sup_v \qty(\ang{p, v} - E(v)) = E^*(p) \\
&\implies \ang{p, u} - E(u) + \ang{q - p, u} \geq E^*(p) + \ang{q - p, u} &\text{for all $q$} \\
&\implies \ang{q, u} - E(u) \geq E^*(p) + \ang{q - p, u} &\text{for all $q$} \\
&\implies \sup_v \qty(\ang{q, v} - E(v)) \geq E^*(p) + \ang{q - p, u} &\text{for all $q$} \\
&\implies E^*(q) \geq E^*(p) + \ang{q -p, u} &\text{for all $q$} \\
&\implies u \in \pt E^*(p). 
		\end{align*}
	Now, for the reverse implication, note that by what we just proved we have
	\[
	u \in \pt E^*(p) \implies p \in \pt E^{**}(u) \iff p \in \pt E(u), 
	\]
	which proves the claim.
		\end{enumerate}
	\end{enumerate}
\end{solution}

\begin{question}
	Let $u, v \in \UU$ and $p \in \pt J(v)$. Recall that the Bregman distance of $J$ at $u, v$ is defined as
	\[
	D_J^p(u, v) \ceq J(u) - J(v) - \ang{p, u - v}.
	\]
	\begin{enumerate}[(a)]
		\item Show that Bregman distances are non-negative. 
		\item Show that Bregman distances may not be symmetric, i.e., there exists a $J$ and $u, v \in \UU$ with $p \in \pt J(v), q \in \pt J(u)$ such that $D_J^p(u, v) \neq D_J^q(v, u)$.
		\item Show that a vanishing Bregman distance may not imply that the two arguments are the same. What if $J$ is strictly convex?
	\end{enumerate}

\end{question}

\begin{proof}
	\begin{enumerate}[(a)]
		\item Since $p \in \pt J(v)$, we have $J(u) \geq J(v) + \ang{p, u - v}$, or equivalently $J(u) - J(v) - \ang{p, u- v} \geq 0$.

		\item Let $\UU = \RR$, $J(x) = \abs{x}$, and choose $u = 0, v = 1$ and $p = 1, q = 0$. Then 
		\[
		D^p_J(u, v) = -1 - (-1) =  0 \quad\text{and}\quad D^q_J(v, u) = 1. 
		\]

		\item In the previous part we had an example $J(x)= \abs{x}, u = 0, v = 1, p = 1$, where $D_J^p(u, v) = 0$ while $u \neq v$.

		Suppose that $J$ is strictly convex and that $u \neq v$ but $D_J^p(u, v) = 0$, so $J(u) = J(v) + \ang{p, u-v}$. Then we have for all $t \in (0, 1)$ that 
		\begin{align*}
			J(v) + \ang{p, (1-t)(u-v)} &= J(v) + \ang{p,  \qty(tv + (1-t)u) -v} \\
			&\overset\star\leq J(tv + (1-t) u) \\
			&< t J(v) + (1-t) J(u) \\
			&= t J(v) + (1-t) \qty(J(v) + (1-t)\ang{p, u-v}) \\
			&= J(v) + \ang{p, (1-t)(u-v)}, 
		\end{align*}
	a contradiction (here $\star$ follows from $p \in \pt J(v)$). We conclude that, if $J$ is strictly convex, the Bregman distance does satisfy $u \neq v \implies D_J^p(u, v) > 0$.

	\end{enumerate}
\end{proof}

>>>>

\item Let $f \in L^1(\Omega) \setminus \BV(\Omega)$, then clearly $\pt \TV(f) = \emptyset$. Now suppose $f \in \BV(\Omega)$.  It is known that the dual of $L^1(\Omega)$ is $L^\infty(\Omega)$. Therefore, we have for $p \in L^\infty(\Omega)$ that 
\begin{align*}
	p \in \pt \TV(f) &\iff \TV(g) \geq \TV(f) + \int_{\Omega} p(x) (g - f)(x) \dd{x} \ \forall g \in L^1(\Omega)
\end{align*}
I do not know how to continue from here. 
\end{enumerate}
\end{solution}
